---
title: "Alcohol Consumption and Grades"
author: "CARTUS YOU"
date: "2018年7月27日"
output: html_document
---

## **Purpose**
Examines whether alcohol consumption has any predictive power over student average grades.

***

> **Preparation**

* Set the working direction and import data.
* Merge the data by columns but not including which related to grdes, since we don't know whether the alcohol assumption have different influence between math and portugueses grades yet.
```{r}
setwd("D:/2018.07 R_DataAnalysis/2018SUMMER_R/data")

ptgs.course <- read.csv("student-por.csv")
math.course <- read.csv("student-mat.csv")

data.source <- merge(ptgs.course,math.course,by=c("school","sex","age","address","famsize","Pstatus",
                                                  "Medu","Fedu","Mjob","Fjob","reason","nursery","internet",
                                                  "guardian","guardian","traveltime","studytime","failures",
                                                  "schoolsup","famsup","activities","higher","romantic",
                                                  "famrel","freetime","goout","Dalc","Walc","health","absences"))
head(data.source)
```
```{r}
summary(data.source)
```

> **EDA**

* Calculate the mean of both grades.
* Change the expression of alcohol assumption.
```{r include=FALSE}
data.source$mathgrades=rowMeans(cbind(data.source$G1.x,data.source$G2.x,data.source$G3.x))
data.source$portgrades=rowMeans(cbind(data.source$G1.y,data.source$G2.y,data.source$G3.y))

library(plyr)
data.source$Dalc <- as.factor(data.source$Dalc)      
data.source$Dalc <- mapvalues(data.source$Dalc, 
                              from = 1:5, 
                              to = c("Very Low", "Low", "Medium", "High", "Very High"))
data.source$Walc <- as.factor(data.source$Walc)      
data.source$Walc <- mapvalues(data.source$Walc, 
                              from = 1:5, 
                              to = c("Very Low", "Low", "Medium", "High", "Very High"))
```

> **Plot**

* Plot a sacatter to see the relationships bwtween alcohol assumption and grades.
* The two scatter plots have few implications:
  1. Among the 85 students, no one consumed high or very high levels of alcohol on daily basis.
  2. Almost all of those who earned relatively high scores consumed very low levels of alcohol on weekdays.
  3. Math and Portuguese grades seem to correlate highly with each other.
```{r}
library(ggplot2)
str1=ggplot(data.source, aes(x=mathgrades, y=portgrades)) +
  geom_point(aes(colour=factor(Dalc)))+ scale_colour_hue(l=25,c=150)+
  geom_smooth(method = "lm", se = FALSE)
str2=ggplot(data.source, aes(x=mathgrades, y=portgrades))+
  geom_point(aes(colour=factor(Walc)))+ scale_colour_hue(l=25,c=150)+
  geom_smooth(method = "lm", se = FALSE)
library(gridExtra)
grid.arrange(str1,str2,nrow=2)
```
* By the implication 3, I think that it's acceptable to combine the two grades together without worrying the lost of features.
* To be cautious, I still calculated the adjusted R squared to make sure it works.
* The R squared is about 0.55, which means that the correlation coefficient between math and Portuguese grades is about 0.74 and that about 55% of the variation in Portuguese grades can be explained by the variation in math grades.
```{r}
r.sqr <- lm(mathgrades ~ portgrades, data=data.source)
print(summary(r.sqr)$r.squared)
print(sqrt(summary(r.sqr)$r.squared))
```

> **Create New Dataframe**

* Combine the original data by rows.
* Create a new column(alcohol) to separate the students into two groups:having alcoholic assumption, and not.
```{r}
library(dplyr)
new.source <-rbind(math.course, ptgs.course) #combine the two datasets
# and eliminate the repeats:
apply.source <- new.source %>% distinct(school,sex,age,address,famsize,Pstatus,Medu,Fedu,Mjob,Fjob,reason,
                                        guardian,traveltime,studytime,failures,schoolsup,
                                        famsup,activities,nursery,higher,internet,romantic,
                                        famrel,freetime,goout,Dalc,Walc,health,absences, .keep_all = TRUE)
apply.source$avggrades <- rowMeans(cbind(apply.source$G1,apply.source$G2,apply.source$G3))
apply.source$alcohol <- apply.source$Dalc + apply.source$Walc
apply.source$alcohol <- as.factor(apply.source$alcohol)
apply.source$alc <- mapvalues(apply.source$alcohol, 
                              from = 2:10,
                              to = c("no","yes","yes","yes","yes","yes","yes","yes","yes"))
head(apply.source)
```


> **T-Test**

* Is having alcoholic assumption or not influence the their academic performance?
* P-value < 0.05
```{r}
t.test(avggrades ~ alc, data=apply.source)
```




