---
title: "0718morning"
author: "CARTUS YOU"
date: "2018年7月19日"
output: html_document
---

## **Basic Assumptions**
   If there is a major disaster happening in the interval, then there should be **relatively more emergency allowances** in that interval, since the press would report the major disaster more often, and the public woulb more concern about the victims, which could urge the government increasing the emergency allowance.

***

> **Preparation**

* Set the working direction and import data.
* DN is the major disaster
```{r}
setwd('D:/2018.07 R_DataAnalysis/2018SUMMER_R/data')

library(readr)
DN <- read_csv("Disaster_NewTaipei.csv")
DNH <- read_csv("Disaster_NewTaipei_Help.csv")
```

> **Organizing Data**

* Turn the time in DN into form as 'xxx.xx'.
* Create weighted sum by Multiplicating.
```{r}
DN$occurrence_time <- substring(as.character(DN$occurrence_time),1,6)
DN$weighted <- as.numeric(as.character(unlist(5*DN[5]+2*DN[6]+2*DN[7]+4*DN[8])))
```

*Create start month and end month for each interval.
```{r}
season <- c(' 全年', ' 第一季', ' 第二季', ' 第三季', ' 第四季')
s_month <- c('.01', '.01', '.04', '.07', '.10')
e_month <- c('.12', '.03', '.06', '.09', '.12')

DNH$startmonth <- gsub(season[1], s_month[1], as.character(DNH$Interval))
DNH$startmonth <- gsub(season[2], s_month[2], as.character(DNH$startmonth))
DNH$startmonth <- gsub(season[3], s_month[3], as.character(DNH$startmonth))
DNH$startmonth <- gsub(season[4], s_month[4], as.character(DNH$startmonth))
DNH$startmonth <- gsub(season[5], s_month[5], as.character(DNH$startmonth))
DNH$startmonth <- as.numeric(DNH$startmonth) - 1911

DNH$endmonth <- gsub(season[1], e_month[1], as.character(DNH$Interval))
DNH$endmonth <- gsub(season[2], e_month[2], as.character(DNH$endmonth))
DNH$endmonth <- gsub(season[3], e_month[3], as.character(DNH$endmonth))
DNH$endmonth <- gsub(season[4], e_month[4], as.character(DNH$endmonth))
DNH$endmonth <- gsub(season[5], e_month[5], as.character(DNH$endmonth))
DNH$endmonth <- as.numeric(DNH$endmonth) - 1911
head(DNH)
```

> **Calculatation**

* Find the rate of possible exaggeration due to the report by adding the percentage of disaster weighted sum in weighted sum in that interval.
```{r}
DNH$weighted <- as.numeric(as.character(unlist(5*DNH[6]+2*DNH[8]+2*DNH[7]+4*DNH[12])))
DNH$exag_rate <- 1
for(i in 1:nrow(DN)){
  for(j in 1:nrow(DNH)){
    if((DNH[j,14] <= DN[i,2]) && (DN[i,2] <= DNH[j,15])){
      DNH[j,17] <- (1 + (DN[i,9] / DNH[j,16]))
    }
  }
}
head(DNH)
```

* Calculate the exaggerated weighted sum and find the average of emergency allowances for each unit.
```{r}
DNH$exaggerated <- as.numeric(as.character(unlist(DNH$weighted * DNH$exag_rate)))
DNH$avg <- as.numeric(as.character(unlist(DNH$Allowance_1000NTD / DNH$exaggerated)))
```


> **Plotting**

* Plot a scatter plot with exaggerated rate and the average of emergency allowance for each unit
* If the assumption is right, the intervals with higher exaggerated rate(in which a major disaster happened) will have a higher average emergency allowance.
```{r}
library(ggplot2)
ggplot(data=DNH, aes(x=exag_rate, y=avg))+
  geom_point(color='violet', size=4)
```


***

## **Conclusion**
  1. The assumption is **wrong** because **we can't see the positive correlation** in the plot.
  2. WHY? Probably becuase 八仙塵暴&復興空難 are **not natural disaster**, which should be subsidize by the government
  3 Instead, the victims of the two disaster could ask for **compensation from the company** which should be responsible for.
  4. Thus, **the compensation is not included in the data, while the amount the victims is**. For the intervals which these two event happended in, though having high exaggerated rate, but the emergency allowance is not higher at all.